Meta-analysis

### 2019-08-09 03_Preliminary_analysis.Rmd
Minor edits

# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(Year >= 2017)%>%
   filter(Fungicide == "control") %>%
ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location))+
   geom_point()+
   geom_smooth()+
   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

# plot table as a box plot

ggplot(PM_MB_means, aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide + as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
     data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))

>>>>

# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(Year >= 2017)%>%
   filter(Fungicide == "control") %>%
ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location))+
   geom_point()+
 #  geom_smooth()+
   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

levels(as.factor(PM_MB_means$Fungicide))
# plot table as a box plot
PM_MB_means %>%
   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
     data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))
